---
title: "ExampleCodes_GT"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R version

```{r}
getRversion()
```


```{r}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("PMassicotte/gtrendsR")

```
```{r}
library(gtrendsR)
library(tidyverse)
library(data.table)
```

## Disclaimer

The gtrendsR package authors are Philippe Massicotte and Dirk Eddelbuettel. These codes are a compilation of my own experience using their package and the help of the open source community online using the gtrendsR package. 

If and when you receive an error code check https://github.com/PMassicotte/gtrendsR/issues or online discussions.


## Obtaining daily data

Selected parameters

Keyword: asylum
Location worldwide (default)
Time range: between 2025-01-01 and 2025-06-30 

```{r}
asylumglobal = gtrends(keyword = "asylum", time = "2025-01-01 2025-06-30",
        gprop = "web", hl = "en", low_search_volume = FALSE)

asylumglobal
```

```{r}
immig = gtrends(keyword = "immigration", time = "2025-01-01 2025-06-30",
        gprop = "web", hl = "en", low_search_volume = FALSE)
```

To save the results for interest over time, following can be used. 

```{r}
gtrends(keyword = "immigration", time = "2025-01-01 2025-06-30",
        gprop = "web", hl = "en", low_search_volume = FALSE, onlyInterest = TRUE)

#or

gtrends(keyword = "immigration", time = "2025-01-01 2025-06-30",
        gprop = "web", hl = "en", low_search_volume = FALSE)$interest_over_time
```

We can define up to 5 different keywords/locations. If we have more than 5 keywords or places to compare, a loop is necessary.

```{r}
data("countries")
countries
SelectedCountries <- c("AU", "TR", "BR", "DE", "EG", "BG", "GE", "IN", "ID", "MX",
                 "CO", "AR")

example <- data.table()

for (i in 1:length(SelectedCountries)) {
    example = rbind(example, (gtrends(keyword = "immigration", geo = SelectedCountries[i],
                              time = "2024-01-01 2024-05-15", gprop = "web",
                              hl = "en", low_search_volume = TRUE))$interest_over_time)
}

```


## Time adjustment

```{r}
library(zoo)
timesd <- c("2025-01-01 2025-06-30", "2024-07-01 2024-12-31", "2024-01-01 2024-06-30") 

example2 = data.table()
for (i in 1:length(timesd)) {
  example2 = rbind(example2, (gtrends(keyword = "refugee", geo = "US",
                                      time = timesd[i], gprop = "web", hl = "en",
                                      low_search_volume = TRUE))$interest_over_time)
  
}
example2 <- example2[order(example2$date)]

examplew <- gtrends(keyword = "refugee", geo = "US",
                     time = "2024-01-01 2025-06-30", gprop = "web", hl = "en",
                     low_search_volume = TRUE)$interest_over_time

# compare the daily and weekly GTI

ggplot(example2, aes(x=as.character(date), y=hits, group=time, color=time)) +
  geom_path() + guides(color=guide_legend(ncol=1)) +
  theme(axis.text.x = element_blank(),axis.title.x = element_blank(),
        panel.grid  = element_blank(),plot.background = element_rect(fill = "gray")) +
  ylab("GTI") + 
  geom_path(data = examplew, aes(x=as.character(date), y=hits, group = time), color = "black")

example2 <- left_join(example2, examplew, by = c("date" = "date",
                                      "keyword" = "keyword",
                                      "geo" = "geo",
                                      "gprop" = "gprop",
                                      "category" = "category")) 

example2 <- rename(example2, dailyhits = hits.x, weeklyhits = hits.y)
example2$scalefactor = example2$weeklyhits / example2$dailyhits

example2 <- example2[1:546,] # to remove the days for which there would be no adjustment factor
example2$scalefactor <- na.locf(example2$scalefactor, fromLast = TRUE)

example2$estimatedhits <- example2$dailyhits * example2$scalefactor
rescale <- function(x){(x-min(x))/(max(x)-min(x)) * 100}
example2 <- example2 %>% mutate(adjustedhits = rescale(estimatedhits))


```

## Keyword as topic: Brisbane vs. Brisbane (city)

```{r}

# as keyword
gtrends(keyword = "Brisbane", time = "2025-01-01 2025-06-30",
        gprop = "web", hl = "en", low_search_volume = TRUE)

# as topic (uses Freebase ID) search in: https://www.wikidata.org
gtrends(keyword = "/m/01b8jj", time = "2025-01-01 2025-06-30",
        gprop = "web", hl = "en", low_search_volume = TRUE)


```



