---
title: "ExampleCodes_GT"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
devtools::install_github("PMassicotte/gtrendsR")
install.packages("gtrendsR")

library(tidyverse)
library(data.table)
```

## Disclaimer

The gtrendsR package authors are Philippe Massicotte and Dirk Eddelbuettel. These codes are a compilation of my own experience using their package and the help of the open source community online using the gtrendsR package. 

If and when you receive an error code check https://github.com/PMassicotte/gtrendsR/issues or online discussions. 

## Obtaining daily data

Selected parameters

Keyword: asylum
Location worldwide (default)
Time range: between 2024-01-01 and 2024-05-15 

```{r}
gtrends(keyword = "asylum", time = "2024-01-01 2024-05-15",
        gprop = "web", hl = "en", low_search_volume = FALSE)
```

A look at related queries suggests asylum may be too broad to be used as a migration proxy.

```{r}
gtrends(keyword = "'temporary protection'", time = "2024-01-01 2024-05-15",
        gprop = "web", hl = "en", low_search_volume = FALSE)
```

To save the results for interest over time, following can be used. 

```{r}
gtrends(keyword = "'temporary protection'", time = "2024-01-01 2024-05-15",
        gprop = "web", hl = "en", low_search_volume = FALSE, onlyInterest = TRUE)

#or

gtrends(keyword = "'temporary protection'", time = "2024-01-01 2024-05-15",
        gprop = "web", hl = "en", low_search_volume = FALSE)$interest_over_time
```

We can define up tp 5 different keywords/locations. If we have more than 5 keywords or places to compare, a loop is necessary.

```{r}
data("countries")
countries
SelectedCountries <- c("CM", "EG", "ET", "GH", "KE", "MW", "MA", "NG", "ZA", "TN",
                 "UG", "ZW")

example <- data.table()

for (i in 1:length(SelectedCountries)) {
    example2 = rbind(example, (gtrends(keyword = "asylum", geo = SelectedCountries[i],
                              time = "2024-01-01 2024-05-15", gprop = "web",
                              hl = "en", low_search_volume = TRUE))$interest_over_time)
}

```

## Time adjustment

```{r}
library(zoo)
timesd <- c("2022-01-01 2022-03-31", "2021-10-01 2021-12-31", "2021-07-01 2021-09-30") 

example = data.table()
for (i in 1:length(timesd)) {
  example = rbind(example, (gtrends(keyword = "refugee", geo = "US",
                                      time = timesd[i], gprop = "web", hl = "en",
                                      low_search_volume = TRUE))$interest_over_time)
  
}
example <- example[order(example$date)]

examplew <- gtrends(keyword = "refugee", geo = "US",
                     time = "2021-07-01 2022-03-31", gprop = "web", hl = "en",
                     low_search_volume = TRUE)$interest_over_time

# compare the daily and weekly GTI

ggplot(example, aes(x=as.character(date), y=hits, group=time, color=time)) +
  geom_path() + guides(color=guide_legend(ncol=1)) +
  theme(axis.text.x = element_blank(),axis.title.x = element_blank(),
        panel.grid  = element_blank(),plot.background = element_rect(fill = "gray")) +
  ylab("GTI") + 
  geom_path(data = examplew, aes(x=as.character(date), y=hits, group = time), color = "black")

example <- left_join(example, examplew, by = c("date" = "date",
                                      "keyword" = "keyword",
                                      "geo" = "geo",
                                      "gprop" = "gprop",
                                      "category" = "category")) 

example <- rename(example, dailyhits = hits.x, weeklyhits = hits.y)
example$scalefactor = example$weeklyhits / example$dailyhits

example <- example[1:270,] # to remove the days for which there would be no adjustment factor
example$scalefactor <- na.locf(example$scalefactor, fromLast = TRUE)

example$estimatedhits <- example$dailyhits * example$scalefactor
rescale <- function(x){(x-min(x))/(max(x)-min(x)) * 100}
example <- example %>% mutate(adjustedhits = rescale(estimatedhits))


```

## Alternative if the above codes don't work

```{r}
keys = c("migration", "residence permit", "asylum")
time = "2024-01-01 2024-05-15"

trendsoutput = list()

for (i in keys) {
trendsoutput = gtrends(keyword=i, gprop ="web", geo="US", time = time, onlyInterest = TRUE, low_search_volume = FALSE)
  Sys.sleep(5)
  results [[i]] = trendsoutput$interest_over_time
}

trends <- do.call("rbind", results)
```

## Keyword as topic: Lilongwe vs. Lilongwe (city)

```{r}

# as keyword
gtrends(keyword = "Lilongwe", time = "2024-01-01 2024-05-15",
        gprop = "web", hl = "en", low_search_volume = TRUE)

# as topic (uses Freebase ID) check: wikidata.org
gtrends(keyword = "/m/0fq7l", time = "2024-01-01 2024-05-15",
        gprop = "web", hl = "en", low_search_volume = TRUE)


```



